Extreme heterogeneity of influenza virus infection in single cells

### 2018-01-16 paper/paper.tex
Fixed a missing comma in methods

\subsection{Flow cytometry titering and analyses}
To determine viral titers in terms of HA-expressing units and for the flow cytometry, A549 cells were seeded in a 6-well plate and infected as described above for the qPCR analyses.
Cells were harvested by trypsinization, resuspended in phosphate-buffered saline supplemented with 2\% heat-inactivated FBS, and stained with 10 \si{\micro}g/ml of H17-L19, a mouse monoclonal antibody confirmed to bind to WSN HA in a prior study~\citep{Doud:2017bw}.
After washing in PBS supplemented with 2\% FBS, the cells were stained with a goat anti-mouse IgG antibody conjugated to APC.
Cells were then washed, fixed in 1\% formaldehyde, and washed further before a final resuspension and analysis. 
We then determined the fraction of cells that were HA positive and calculated the HA-expressing units.
For NS1 staining, cells stained for HA as described above were permeabilized using BD Cytofix/Cytoperm following manufacturer's instructions, stained with anti-NS1 (GTX125990, Genetex) at 4.4 \si{\micro}g/ml, washed,  stained with a  goat anti-rabbit IgG antibody conjugated to Alexa Fluor 405. washed, and analyzed.
To analyze the effect of N-acetylcysteine, the compound was added to cells in D10 9h prior to media change and infection, and included in infection media.
Stocks of N-acetylcysteine were reconstituted immediately prior to use, and the pH of growth media supplemented with this compound was adjusted using sodium hydroxide.
After channels were compensated and cells gated to exclude multiplets and debris in FlowJo, data were extracted using the R package flowCore~\citep{LeMeur:2007uo} and analyzed using a custom Python script.
Guassian kernel density estimates were obtained using the scipy stats package method, guassian\_kde, using automatic bandwidth determination~\citep{vanderWalt:2017dp}.
For gating on NS1 positive cells, the percentage of influenza-infected cells was determined by HA staining alone, and the top quantile of NS1-stained cells matching that percentage were taken as the NS1 positive population.

>>>>

\subsection{Flow cytometry titering and analyses}
To determine viral titers in terms of HA-expressing units and for the flow cytometry, A549 cells were seeded in a 6-well plate and infected as described above for the qPCR analyses.
Cells were harvested by trypsinization, resuspended in phosphate-buffered saline supplemented with 2\% heat-inactivated FBS, and stained with 10 \si{\micro}g/ml of H17-L19, a mouse monoclonal antibody confirmed to bind to WSN HA in a prior study~\citep{Doud:2017bw}.
After washing in PBS supplemented with 2\% FBS, the cells were stained with a goat anti-mouse IgG antibody conjugated to APC.
Cells were then washed, fixed in 1\% formaldehyde, and washed further before a final resuspension and analysis. 
We then determined the fraction of cells that were HA positive and calculated the HA-expressing units.
For NS1 staining, cells stained for HA as described above were permeabilized using BD Cytofix/Cytoperm following manufacturer's instructions, stained with anti-NS1 (GTX125990, Genetex) at 4.4 \si{\micro}g/ml, washed,  stained with a  goat anti-rabbit IgG antibody conjugated to Alexa Fluor 405, washed, and analyzed.
To analyze the effect of N-acetylcysteine, the compound was added to cells in D10 9h prior to media change and infection, and included in infection media.
Stocks of N-acetylcysteine were reconstituted immediately prior to use, and the pH of growth media supplemented with this compound was adjusted using sodium hydroxide.
After channels were compensated and cells gated to exclude multiplets and debris in FlowJo, data were extracted using the R package flowCore~\citep{LeMeur:2007uo} and analyzed using a custom Python script.
Guassian kernel density estimates were obtained using the scipy stats package method, guassian\_kde, using automatic bandwidth determination~\citep{vanderWalt:2017dp}.
For gating on NS1 positive cells, the percentage of influenza-infected cells was determined by HA staining alone, and the top quantile of NS1-stained cells matching that percentage were taken as the NS1 positive population.
